l

### 2023-03-31 resume/Resume.tex
Deploying to gh-pages from @ JasonGross/JasonGross.github.io@40bb8bd01b90aaf91b9564c15f587273acc75411 🚀

% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[11pt]{res}
\usepackage[T1]{fontenc}
\usepackage{xifthen,verbatim}
\usepackage{hyperref}
\usepackage{etoolbox}[2011/01/03]

\usepackage[backend=biber,bibencoding=utf-8,maxbibnames=99,sorting=ymdnt,noerroretextools=true,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}

\makeatletter

\let\origifempty\ifempty
\undef\ifempty
\let\origforlistloop\forlistloop
\usepackage{etextools}
\let\eifempty\ifempty
\let\ifempty\origifempty
\let\forlistloop\origforlistloop
\def\preetextools{\let\ifempty\eifempty}

\newif\ifmultitexcompile
\multitexcompiletrue

\newcommand\multitex@separator{-}
\newwrite\multitex@temp
% \immediate\openout\multitex@temp{\jobname.mtx}
\newtoks\multitex@names
\multitex@names={}
\newcommand{\multitex@postprocess}[1]{%
  \immediate\expandafter\closeout\csname @multitex@#1@file\endcsname
  \ifmultitexcompile
    \immediate\write18{pdflatex \csname @multitex@#1@name\endcsname}%
    \immediate\write18{biber \csname @multitex@#1@barename\endcsname}%
    \immediate\write18{pdflatex \csname @multitex@#1@name\endcsname}%
  \fi
}
\newcommand{\onlymultitex}[1]{\FE@ifstar{#1}{\only@other@multitex}{\only@multitex}}
\newcommand{\only@multitex}[2]{#2}
\newcommand{\only@other@multitex}[2]{}
{\catcode`\#=12
  \global\def\@pound{#}
}
\newcommand{\DeclareFile}[2][]{
  \global\multitex@names=\expandafter{\the\multitex@names,#2}
  \expandafter\xdef\csname @multitex@#2\endcsname{\xifempty{#1}{#2}{#1}}
  \expandafter\xdef\csname @multitex@#2@name\endcsname{"\jobname\multitex@separator\csname @multitex@#2\endcsname.tex"}
  \expandafter\xdef\csname @multitex@#2@auxname\endcsname{"\jobname\multitex@separator\csname @multitex@#2\endcsname.aux"}
  \expandafter\xdef\csname @multitex@#2@barename\endcsname{"\jobname\multitex@separator\csname @multitex@#2\endcsname"}
  \expandafter\newwrite\csname @multitex@#2@file\endcsname
  \immediate\expandafter\openout\csname @multitex@#2@file\expandafter\endcsname\csname @multitex@#2@name\endcsname
  \AtBeginDocument{%
    \multitex@write{#2}{%
      \detokenize{\newcommand{\onlymultitex}[1]}%
        {\detokenize{\csname FE@ifstar\endcsname}%
          {\@pound1}%
          \detokenize{%
            {\csname only@multitex\endcsname}{\csname only@multitex\endcsname}%
          }%
        }%
      \detokenize{%
        \expandafter\newcommand\csname only@multitex\endcsname[2]}%
        {%
          \noexpand\renewcommand*{\noexpand\do}[1]{%
            \noexpand\ifstrequal{\@pound\@pound1}{#2}%
              {\@pound2\noexpand\listbreak}%
              {}%
            }%
          {\noexpand\edef\noexpand\foo{\@pound1}\noexpand\expandafter}%
          \noexpand\expandafter\noexpand\docsvlist\noexpand\expandafter{\noexpand\foo}%
        }
      \detokenize{%
        \expandafter\let\csname only@other@multitex\expandafter\endcsname\csname only@multitex\endcsname
      }%
    }%
  }
  \AtEndDocument{\multitex@postprocess{#2}}
}
\newcommand{\multitex@write}[2]{\xifblank{#1}{}{\immediate\expandafter\write\csname @multitex@#1@file\endcsname{#2}}}
\edef\multitex@tempfilename{\jobname.mtx}
\newcommand{\multitex@pre@writetothis}{\immediate\openout\multitex@temp\multitex@tempfilename}%\long\gdef\multitex@thiscode{}}%
\newcommand{\multitex@writetothis}[1]{\immediate\write\multitex@temp{#1}}%\ExpandNext{\long\gappto\multitex@thiscode}{\expandnext{\relax\scantokens}{#1}}}%
\newcommand{\multitex@post@writetothis}{\immediate\closeout\multitex@temp\relax\input{\multitex@tempfilename}}%\show\multitex@thiscode\multitex@thiscode\relax}%
\newcommand{\multitex@writetoothers}[2][\the\multitex@names]{{\preetextools\ExpandNext{\forcsvloop}{#1}\do{\multitex@write{##1}{#2}}}}
\newcommand{\DeclareDocumentClass}[1]{\multitex@writetoothers{\detokenize{#1}}}
\AtBeginDocument{\multitex@writetoothers{\detokenize{\begin{document}}}}
\AtEndDocument{\multitex@writetoothers{\detokenize{\end{document}}}}
\newcommand{\includein}[2][]{\multitex@pre@writetothis\multitex@writetothis{\detokenize{#2}}\multitex@post@writetothis\multitex@writetoothers[#1]{\detokenize{#2}}}
\AfterEndEnvironment{multitex}{\multitex@post@writetothis}
\newenvironment{multitex}[1][\the\multitex@names]{%
  \@bsphack
  \begingroup% Lets Keep the Changes Local
    \multitex@pre@writetothis
    \let\do\@makeother\dospecials\catcode`\^^M\active
    \def\verbatim@processline{\multitex@writetothis{\the\verbatim@line}\multitex@writetoothers[#1]{\the\verbatim@line}}%
    \verbatim@start\space % I'm not sure why I need the space, but I seem to need it.
}{\endgroup
  \@esphack
}
% only others
\newenvironment{multitex*}[1][\the\multitex@names]{%
  \@bsphack
  \begingroup% Lets Keep the Changes Local
    \let\do\@makeother\dospecials\catcode`\^^M\active
    \def\verbatim@processline{\multitex@writetoothers[#1]{\the\verbatim@line}}%
    \verbatim@start\space % I'm not sure why I need the space, but I seem to need it.
}{\endgroup
  \@esphack
}
\makeatother

\DeclareFile{curriculum-vitae}
%\DeclareFile{mathematics}
%\DeclareFile{computer-science}
%\DeclareFile{curriculum-vitae-long}
%\DeclareFile{curriculum-vitae-mathematics}
%\DeclareFile{curriculum-vitae-computer-science}
\DeclareDocumentClass{\documentclass[11pt]{res}}

\begin{multitex}
  \edef\resumefiles{mathematics,computer-science}
  \edef\cvshortspecialfiles{curriculum-vitae-mathematics,curriculum-vitae-computer-science}
  \edef\cvshortfiles{curriculum-vitae,\cvshortspecialfiles}
  \edef\cvlongfiles{curriculum-vitae-long}
  \edef\cvfiles{\cvshortfiles,\cvlongfiles}
  \edef\highschoolfiles{curriculum-vitae-long}
  \edef\mathfiles{mathematics,curriculum-vitae-mathematics}
  \edef\cvlongandmathfiles{\mathfiles,curriculum-vitae-long}
  \edef\cvandmathfiles{\cvlongandmathfiles,curriculum-vitae,curriculum-vitae-computer-science}
  \edef\computersciencefiles{computer-science,curriculum-vitae-computer-science}
  \edef\cvlongandcomputersciencefiles{\computersciencefiles,curriculum-vitae-long}
  \edef\cvandcomputersciencefiles{curriculum-vitae,curriculum-vitae-mathematics,\cvlongandcomputersciencefiles}
  \edef\allexceptcv{\resumefiles,\cvshortspecialfiles}
  \edef\allexceptcvlongfiles{\resumefiles,\cvshortfiles}
  \edef\allexceptcvandcvlongfiles{\resumefiles,\cvshortspecialfiles}
  %\usepackage[utf8x]{inputenc}
  %\usepackage[T1]{fontenc}
  %\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
  %\usepackage{newcent}   % uses new century schoolbook postscript font
  \usepackage[T1]{fontenc}
  \usepackage[margin=1in,top=0.5in,bottom=0.5in]{geometry}
  \usepackage{hyperref}
  \usepackage{calc}
  \usepackage{amsmath}
  \usepackage{etoolbox}[2011/01/03]
  %\bibliographystyle{plainyr-rev}
  \usepackage[backend=biber,maxbibnames=99,sorting=ymdnt,noerroretextools=true,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}
  \addbibresource{jason-gross.bib}
  \DeclareBibliographyCategory{exclude}
  \makeatletter
  \@ifpackageloaded{etextools}{%
  }{%
    \let\origifempty\ifempty
    \let\origforlistloop\forlistloop
    \undef\ifempty
    \usepackage{etextools}
    \let\eifempty\ifempty
    \let\ifempty\origifempty
    \let\forlistloop\origforlistloop
    \def\preetextools{\let\ifempty\eifempty}
  }%
  \makeatother
  \begin{format}
    \employer{l}\dates{r}\\
    \title{l}\location{r} \\
    \body
  \end{format}
  \let\oldemployer=\employer
  \let\oldtitle=\title
  \renewcommand{\employer}[1]{\oldemployer{\textbf{#1}}}
  \renewcommand{\title}[1]{\oldtitle{\textit{#1}}}

@@

  \newsectionwidth{1em}
  \resumewidth=7.5in

  \newcommand{\aswidthof}[2]{\rlap{#1}\hphantom{#2}}
\end{multitex}

\begin{multitex}
  \name{\LARGE \bf \parbox{\widthof{github.com/JasonGross}}{%
      \centering Jason Gross \\
      \vspace{0.2cm}
      \large \href{https://github.com/JasonGross/}{github.com/JasonGross} \\
      \href{https://people.csail.mit.edu/jgross/}{people.csail.mit.edu/jgross} \\
      $\left.\right.$ \\
      $\left.\right.$ \\%
  }}

@@

  %\address{}%\textsc{Address}\\258 Prospect Street, Apt \# 1L\\Cambridge, MA 02139}
  %\address{\textsc{Contact}\\\href{mailto:jgross@mit.edu}{jgross@mit.edu}\\(631) 790-8962}
  \newcommand{\addressaswidth}[1]{\makebox[\widthof{\textsc{jgross@mit.edu}}][c]{#1}}
  \address{\addressaswidth{\textsc{Contact}}\\\addressaswidth{\href{mailto:jgross@mit.edu}{jgross@mit.edu}}\\\addressaswidth{(631) 790-8962}}
\end{multitex}

@@

\begin{multitex}
  \resume

@@

  \begin{itemize}
  \item MIRI, summer 2019: Formalized type theories, and proved properties of programs that reason about themselves
  \item Google, summer 2018: Worked on integration of Fiat Cryptography with BoringSSL in Chrome
  \item Google, summer 2016: Extended Fiat Cryptography with ECC primiatives for integration with Open Titan
  \item Microsoft Research, summer 2014: Collaboratively created a language for specifying input/output behavior of x86 assembly programs, verfied the input/output behavior of a number of simple programs, and improved performance of the x86proved project
  \item MIT CSAIL - PLV, 2012 - 2014: Entered a significant amount of category theory into the automated proof assistant Coq, and worked on building an interface for databases and database migration on top of category theory 
  \item MIT CSAIL - CoCoSci, 2009 - 2011: Designed and managed the data collection webpage for research in categorical learning and transfer learning
  \item Commack High School, 2006 - 2009: Researched circuits over sets of natural numbers, winning 4th (2009) and 3rd (2008) place awards in mathematics at ISEF
  \end{itemize}

@@

  \section{\textsc{Programming Languages}}
  \begin{itemize}
  \item
    Proficient: Coq, \onlymultitex{\cvlongfiles}{\TeX{} macro language, }Mathematica, git, Python, JavaScript, BASIC
  \item
    Working knowledge: \onlymultitex{\cvlongfiles}{\LaTeX{}, }C, C++, Agda, OCaml, Haskell, Scheme, HTML, CSS, Perl, Java
  \item
    Basic knowledge: Matlab, Lean, Idris, Ruby, Go, Ur/Web, x86 Assembly
  \end{itemize}

@@

  \endresume
\end{multitex}
\end{document}

>>>>

\documentclass[11pt]{res}

\usepackage[T1]{fontenc}
\usepackage[margin=1in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{calc}
\usepackage{amsmath}
\usepackage{etoolbox}[2011/01/03]
\usepackage[backend=biber,maxbibnames=99,sorting=ymdnt,noerroretextools=true,style=alphabetic]{biblatex}
% http://tex.stackexchange.com/a/140641
\DeclareSortingTemplate{ymdnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{sortyear}
        \field{year}
        \literal{9999}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{day}
        \literal{99}
    }
    \sort{
        \field{sortname}
        \field{author}
        \field{editor}
        \field{translator}
        \field{sorttitle}
        \field{title}
    }
    \sort{
        \field{sorttitle}
        \field{title}
    }
}
\addbibresource{jason-gross.bib}
\DeclareBibliographyCategory{exclude}
\makeatletter
\@ifpackageloaded{etextools}{%
}{%
  \let\origifempty\ifempty
  \let\origforlistloop\forlistloop
  \undef\ifempty
  \usepackage{etextools}
  \let\eifempty\ifempty
  \let\ifempty\origifempty
  \let\forlistloop\origforlistloop
  \def\preetextools{\let\ifempty\eifempty}
}%
\makeatother
\begin{format}
  \employer{l}\dates{r}\\
  \title{l}\location{r} \\
  \body
\end{format}
\let\oldemployer=\employer
\let\oldtitle=\title
\renewcommand{\employer}[1]{\oldemployer{\textbf{#1}}}
\renewcommand{\title}[1]{\oldtitle{\textit{#1}}}

@@

\newsectionwidth{1em}
\makeatletter
\pretocmd{\employer}{\vskip-\baselineskip}{}{}
\apptocmd{\@@section}{\vskip1.5\baselineskip\relax}{}{}
\makeatother
\resumewidth=7.5in

\newcommand{\aswidthof}[2]{\rlap{#1}\hphantom{#2}}

\name{\LARGE \bf \parbox{\widthof{github.com/JasonGross}}{%
    \centering Jason Gross \\
    \vspace{0.2cm}
    \large \href{https://github.com/JasonGross/}{github.com/JasonGross} \\
    \href{https://people.csail.mit.edu/jgross/}{people.csail.mit.edu/jgross} \\
    $\left.\right.$ \\
    $\left.\right.$ \\%
}}

@@

%\address{}%\textsc{Address}\\258 Prospect Street, Apt \# 1L\\Cambridge, MA 02139}
%\address{\textsc{Contact}\\\href{mailto:jgross@mit.edu}{jgross@mit.edu}\\(631) 790-8962}
\newcommand{\addressaswidth}[1]{\makebox[\widthof{\textsc{jgross@mit.edu}}][c]{#1}}
\address{\addressaswidth{\textsc{Contact}}\\\addressaswidth{\href{mailto:jgross@mit.edu}{jgross@mit.edu}}\\\addressaswidth{(631) 790-8962}}

@@

\resume

@@

\begin{itemize}
\item MIRI, summer 2019: Formalized type theories, and proved properties of programs that reason about themselves
\item Google, summer 2018: Worked on integration of Fiat Cryptography with BoringSSL in Chrome
\item Google, summer 2016: Extended Fiat Cryptography with ECC primiatives for integration with Open Titan
\item Microsoft Research, summer 2014: Collaboratively created a language for specifying input/output behavior of x86 assembly programs, verfied the input/output behavior of a number of simple programs, and improved performance of the x86proved project
\item MIT CSAIL --- PLV, 2012--2014: Entered a significant amount of category theory into the automated proof assistant Coq, and worked on building an interface for databases and database migration on top of category theory
\item MIT CSAIL --- CoCoSci, 2009--2011: Designed and managed the data collection webpage for research in categorical learning and transfer learning
\item Commack High School, 2006--2009: Researched circuits over sets of natural numbers, winning 4th (2009) and 3rd (2008) place awards in mathematics at ISEF
\end{itemize}

@@

\section{\textsc{Programming Languages}}
\begin{itemize}
\item
  Proficient: Coq, %\onlymultitex{\cvlongfiles}{\TeX{} macro language, }
  Mathematica, git, Python, JavaScript, BASIC
\item
  Working knowledge: %\onlymultitex{\cvlongfiles}{\LaTeX{}, }
  C, C++, Agda, OCaml, Haskell, Scheme, HTML, CSS, Perl, Java
\item
  Basic knowledge: Matlab, Lean, Idris, Ruby, Go, Ur/Web, x86 Assembly
\end{itemize}

@@

\endresume
\end{document}
